Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-26 paper/paper.tex
ground truth section

\subsubsection{Ground Truth.}To evaluate precision of \tname\ we
need rules that are considered correct to use as reference. The rules
that detect the attacks from Table~\ref{table:attacks} were obtained
from the Emerging Threats Open Ruleset~\cite{emerging-threats-open}.

>>>>

\subsubsection{Ground Truth.}To evaluate \tname\ objectively we need
to compare the rules it generates with human-written rules from a
trusted source. We used the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open} data set for that. After
finding the attack and corresponding rule using the procedure
described in Section~\ref{subsec:malicious-traffic}, we reproduced the
attack and confirmed that the rule captures the attack. Column
``Ground Truth'' from Table~\ref{table:attacks} only shows the
essential relevant options. Documentation options (\eg{}, ``msg'') are
discared.
